### 2015-02-10 fundamentals/examples.tex
adds a wrapup paragraph to @rwcarlsen examples section.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker1963comparison}.  This technique has also been used in the
        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
        Commissariat \`{a} l'\'{e}nergie atomique (CEA).

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
1-pass and inifinite-pass cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
recycle scenario does not re-recycle material, it takes the fabrication
facility 2 cycles longer to accumulate a full batch of fissile material.

@@

>>>>

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        Commelini-Sicart (COSI) fuel cycle simulator developed by the French
        Commissariat \`{a} l'\'{e}nergie atomique (CEA).

@@

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for once
through (no recycle), 1-pass recycle, and infinite-pass recycle variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
1-pass and infinite-pass cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the 1-pass recycle case and every 9
cycles (180 months) for the infinite-pass recycle case.  Because the 1-pass
recycle scenario does not re-recycle material, it takes the fabrication
facility 2 cycles longer to accumulate a full batch of fissile material.

@@

The fundamental capabilities of demonstrated in these simulations qualify
\Cyclus and its ecosystem to model the breadth of scenario types expected of
nuclear fuel cycle simulator tools. These examples further show the flexibility
provided by the material routing logic within the \Cyclus framework and provide
an example of the resolution made possible by discrete-facility and
discrete-material modeling in fuel cycle simulation.
